---
title: "SVD score instrument"
date: 2023-01-02
author: Andreas Gammelgaard Damsbo
editor: visual
toc: true
bibliography: references.bib
---

```{r}
#| echo: false
readr::write_csv(REDCapR::redcap_metadata_read(redcap_uri = "https://redcap.au.dk/api/",token = keyring::key_get("SVD_REDCAP_API"))$data,here::here("data/svd-datadictionary.csv"))
```

# Clinical data

Minimal necessary clinical data for scoring are pooled and uploaded to a
separate data base.

The scripts used are fairly trivial, but can serve as inspirational. The
functions used can [be found here](R/functions.R).

The simple pipeline is as follows

```{r}
#| eval: false
source(here::here("R/functions.R"))
ds |> # The data set retrieved from the relevant data base
  # filter_talos_site() |>
  modify_data() |>
  write2new_db()
```

# Using REDCap

All clinical data capturing for this project is performed with
[REDCap](https://projectredcap.org/).

Get our most recent [data dictionary here](data/svd-datadictionary.csv)
to use in your own project. Note that the text on a few fields are in
Danish.

The dictionary can be previewed below:

```{r}
readr::read_csv(here::here("data/svd-datadictionary.csv")) |> gt::gt()
```
